--- 
title: "R Markdown Output"
subtitle: "Last run on:\n `r Sys.time()`"
date: "`r Sys.time()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: book.bib
biblio-style: apalike
link-citations: yes
description: "An example of a bookdown document using R Markdown"
---

# Overview

This document has code embedded throughout. In the next section we will create a visualization using the already loaded dataset `eth_data`:
```{r, warning=F, message=F}
datatable(eth_data)
```

The table above uses the **`DT`** package [@R-DT]. The **`bookdown`** package [@R-bookdown] is packed with functionality, including in-text citations that automatically generate the references as we have done here.



<!--chapter:end:index.Rmd-->

# Price Chart - Ethereum

```{r, warning=F, message=F, echo=F}
eth_chart
```

<!--chapter:end:01-chart_example.Rmd-->

# Python Code Example

```{python}
import pandas as pd
# Create the Python object from R
df = r.cryptodata
# Show the new Python dataframe
df
```

## One more Python example

The code below creates a new column `price_percentile` that specifies if the price for the row was in the upper or lower 50th percentile of prices (BTC should be upper and ETH lower):

```{python}
import numpy as np
# Create a new column based on the ask_1_price value:
df['price_percentile'] = np.where(df['ask_1_price'] > 
                                  np.percentile(df['ask_1_price'], 50),
                            'upper 50th percentile of prices', 
                            'lower 50th percentile of prices')
# Show modified dataframe:
df[['symbol', 'ask_1_price', 'price_percentile']]
```

<!--chapter:end:02-python_example.Rmd-->

# bookdown Examples

- [See this example for a more complex bookdown document which updates automatically every 12 hours using the same tools as this example.](https://cryptocurrencyresearch.org/)

- [Supervised Machine Learning for Text Analysis in R](https://smltar.com/)

- [JavaScript for R](https://book.javascript-for-r.com/)

**Find more examples published through the bookdown website: https://bookdown.org/home/archive/**

<!--chapter:end:03-bookdown_examples.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:04-references.Rmd-->

