---
title: "R Markdown Output"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=F}
# Import packages
library(pacman)
library(pins)
library(tidyverse)
library(DT)
library(ggforce)
library(ggthemes)
library(ggpubr)

# Pull data - first register pins board to establish connection
board_register("https://raw.githubusercontent.com/predictcrypto/pins/master/","hitBTC_orderbooks_github")
# Only keep main cryptocurrencies BTC and ETH
cryptodata <- select(pin_get("hitBTC_orderbooks_github", "hitBTC_orderbooks_github"),
                     pair, symbol, ask_1_price, date_time_utc)
# Arrange data from latest to earliest
cryptodata <- arrange(cryptodata, desc(date_time_utc))
```

## Topic 1

### Example [ADD]
Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

## Topic 2

### Python code example




### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question_checkbox("Which lanuguages (among many others) are supported by R Markdown?",
    answer("python", correct = TRUE),
    answer("sql", correct = TRUE),
    answer("css", correct = TRUE),
  random_answer_order = TRUE,
  allow_retry = TRUE
  ),
  question("Isn't R Markdown awesome?",
    answer("yes!", correct = TRUE),
    answer("no")
  )
)
```

