---
title: "R Markdown Output"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=F}
# Import packages
library(pacman)
library(pins)
library(tidyverse)
library(DT)
library(ggforce)
library(ggthemes)
library(ggpubr)
library(learnr)
library(knitr)

# Pull data - first register pins board to establish connection
board_register("https://raw.githubusercontent.com/predictcrypto/pins/master/","hitBTC_orderbooks_github")
# Only keep main cryptocurrencies BTC and ETH
cryptodata <- select(pin_get("hitBTC_orderbooks_github", "hitBTC_orderbooks_github"),
                     pair, symbol, ask_1_price, date_time_utc)
# Arrange data from latest to earliest
cryptodata <- arrange(cryptodata, desc(date_time_utc))
# disable scientific notation
options(scipen = 999)
```

## Overview

This document has code embedded throughout and was created using the [R package **learnr**](https://rstudio.github.io/learnr/). In the next section we will create a visualization using the already loaded dataset `cryptodata`.

Click on the blue button "run code" below. You can add to the code below and run it; click on the button "Hint" below for an example filtering the data down to only rows with the cryptocurrency symbol "ETH" for the Ethereum cryptocurrency. Once you write your code make sure to click on the blue button that says "Run Code" to refresh the results shown.

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
cryptodata
```

```{r print-limit-hint}
filter(cryptodata, symbol == 'ETH')
```

Feel free to play around with the code chunk above and run whatever R code you would like on the data.

For example, here is same price chart shown in all other examples, you could copy and paste the code above and make changes as you please:
```{r, warning=F, message=F}
ggplot(filter(cryptodata, symbol == 'ETH'), 
       aes(x = date_time_utc, y = ask_1_price)) +
  # show points as a line
  geom_line() + 
  # Add trend line
  stat_smooth() +
  # Add labels
  xlab('Date Time (UTC)') +
  ylab('Price ($)') +
  ggtitle(paste('Price Change Over Time - ETH'),
          subtitle = paste('Most recent data collected on:',
                     max(cryptodata$date_time_utc, na.rm=T), '(UTC)')) + 
  # Add theme
  theme_economist() + 
  # Add regression stats
  stat_cor() +
  # Circle max price
  geom_mark_ellipse(aes(filter = ask_1_price == max(ask_1_price),
                        label = date_time_utc,
                        description = paste0('Price spike to $', ask_1_price))) +
  # Now the same to circle the minimum price
  geom_mark_ellipse(aes(filter = ask_1_price == min(ask_1_price),
                        label = date_time_utc,
                        description = paste0('Price drop to $', ask_1_price)))
```

## Example Quiz

*You can include any number of single or multiple choice questions as a quiz*

Learn more about using this package here: https://rstudio.github.io/learnr/

```{r quiz, echo=F}
quiz(
  question_checkbox("Which lanuguages (among many others) are supported by R Markdown?",
    answer("python", correct = TRUE),
    answer("sql", correct = TRUE),
    answer("css", correct = TRUE),
  random_answer_order = TRUE,
  allow_retry = TRUE
  ),
  question("One more example with one option:",
    answer("correct", correct = TRUE),
    answer("wrong answer")
  )
)
```


## Python Code Example

Like the other examples, we can run Python code

```{python}
import pandas as pd
# Create the Python object from R
df = r.cryptodata
# Show the new Python dataframe
df
```

### One more Python example

The code below creates a new column `price_percentile` that specifies if the price for the row was in the upper or lower 50th percentile of prices (BTC should be upper and ETH lower):

```{python}
import numpy as np
# Create a new column based on the ask_1_price value:
df['price_percentile'] = np.where(df['ask_1_price'] > 
                                  np.percentile(df['ask_1_price'], 50),
                            'upper 50th percentile of prices', 
                            'lower 50th percentile of prices')
# Show modified dataframe:
df[['symbol', 'ask_1_price', 'price_percentile']]
```

There is also a way of allowing users to run Python code as exercise code chunks, see this thread for more information: https://github.com/rstudio/learnr/issues/213

## [Back to Gallery](https://r-markdown-gallery.org)

```{r}
include_url("https://r-markdown-gallery.org")
```

