---
title: "Example Presentation"
output: ioslides_presentation
---

## Overview

This document has code embedded throughout. In the next section we will create a visualization using the already loaded dataset `cryptodata`:
```{r, warning=F, message=F}
datatable(cryptodata, rownames = FALSE, 
          options(list(lengthMenu = c(4, 5, 6))))
```

## Price Chart

```{r, warning=F, message=F, echo=F}
crypto_chart
```


## Interactive Chart

```{r, warning=F, message=F, echo=F}
interactive_chart
```

## Python Code Example

```{python}
import pandas as pd
# Show the R data from Python
r.cryptodata
```

## One more Python example

Press on `w` on your keyboard to make the presentation wider. Press `f` to fullscreen.

```{python}
import numpy as np
# Create a new field based on the price value:
df['price_percentile'] = np.where(df['ask_1_price'] > np.percentile(df['ask_1_price'], 50),
                            'upper 50th percentile of prices', 
                            'lower 50th percentile of prices')
# Show modified dataframe:
df[['symbol', 'ask_1_price', 'price_percentile']]
```

## Back to Gallery

TODO - Add note about going back to gallery
