---
title: "R Markdown Output"
output: revealjs::revealjs_presentation
subtitle: "Last run on:\n `r Sys.time()`"
---

# Overview

This document has code embedded throughout. In the next section we will create a visualization using the already loaded dataset `eth_data`:
```{r, warning=F, message=F}
datatable(eth_data, options = list(lengthMenu = c(3, 5, 10)))
```

# Price Chart - Ethereum

```{r, warning=F, message=F, echo=F}
eth_chart
```

## Price Chart - Bitcoin

```{r, warning=F, message=F, echo=F}
ggplot(data = filter(cryptodata, symbol == 'BTC'), 
                       aes(x = date_time_utc, y = ask_1_price)) + 
                # show points as a line
                geom_line() + 
                # Add trend line
                stat_smooth() +
                # Add labels
                xlab('Date Time (UTC)') +
                ylab('Price ($)') +
                ggtitle(paste('Price Change Over Time - BTC'),
                        subtitle = paste('Most recent data collected on:',
                                   max(eth_data$date_time_utc, na.rm=T), '(UTC)')) + 
                # Add theme
                theme_economist() + 
                stat_cor() +
                geom_mark_ellipse(aes(filter = ask_1_price == max(ask_1_price),
                                      label = date_time_utc,
                                      description = paste0('Price spike to $', ask_1_price))) +
                  # Now the same to circle the minimum price:
                geom_mark_ellipse(aes(filter = ask_1_price == min(ask_1_price),
                                      label = date_time_utc,
                                      description = paste0('Price drop to $', ask_1_price)))
```


# Python Code Example

```{python}
import pandas as pd
# Create the Python object from R
df = r.cryptodata
# Show the new Python dataframe
df
```

Press on the ⬇️ key on your keyboard for next slide

## One more Python example

The code below creates a new column `price_percentile` that specifies if the price for the row was in the upper or lower 50th percentile of prices (BTC should be upper and ETH lower):

```{python}
import numpy as np
# Create a new column based on the ask_1_price value:
df['price_percentile'] = np.where(df['ask_1_price'] > 
                                  np.percentile(df['ask_1_price'], 50),
                            'upper 50th percentile of prices', 
                            'lower 50th percentile of prices')
# Show modified dataframe:
df[['symbol', 'ask_1_price', 'price_percentile']]
```

